% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Patrick Yu}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
A9\\
130 Lytton Avenue \#300\\
Palo Alto, CA 94301}


\begin{flushleft}
{\large\bf Patrick Yu}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 2515 Benvenue Ave, Apt 309, Berkeley, California 94704 \\
\hfill (714) 651 - 5438
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear A9:} 
 
\noindent I am writing to apply to your Software Engineer - Visual Search. This May I am going to be finishing what has been an enlightening experience at the University of California, Berkeley.  One of your recruiters at my university encouraged me to apply to this position.

\noindent I have an interest in this position for a couple of different reasons. First, I am an Applied Mathematics major with a Computer Science concentration. I have a strong background in both Python and Java and have taken multiple classes which have required me to use both. Second, I have a background in statistical computing with data where I used R to work with large data sets to analyze information. Moreover, I communicate with my peers effectively and have served as a leader in community service organizations. Finally, one of the biggest reasons I am interested in working with A9 is my love for difficult problems. In my time at Berkeley, I learned that I love to challenge myself. I switched into a more difficult major, did not hesitate to take demanding classes, and did all I could to demand more of myself. I want to continue to find opportunities to challenge myself after I graduate, and I know that working at A9 will provide that for me.

\noindent My roomate, Kenneth Do, interned with you over the summer and had only good things to say about what he did and learned. I hope to have a similar experience.  Please feel free to ask me any questions - my contact information can be found here and on my resume. Also, I am located just across the Bay, so I am just a stone's throw away. Thank you for your consideration and time.
 
\closing{Sincerely yours,} 
 

 

\end{letter}
 

\end{document}






