% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Patrick Yu}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{
MyVest\\
500 Howard St. Suite 425\\
San Francsico, CA 94105}

\begin{flushleft}
{\large\bf Patrick Yu}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 2515 Benvenue Ave, Apt 309, Berkeley, California 94704 \\
\hfill (714) 651 - 5438
\end{flushright} 
\vfill % forces letterhead to top of page

 
\opening{Dear MyVest:} 
 
\noindent I am writing to apply to your Entry Level Software Engineer position. This May I am going to be finishing what has been an enlightening experience at the University of California, Berkeley.  I spoke with one of your team members at UC Berkeley's Career Fair.

\noindent I have an interest in this position for a couple of different reasons. First, I am an Applied Mathematics major with a Computer Science concentration. I have a strong background in both Python and Java and have taken multiple classes which have required me to use both.  I also have programming experience in many other languages.  Second, I communicate with my peers effectively and have served as a leader in community service organizations. Finally, one of the biggest reasons I am interested in working with MyVest is my love for difficult problems. In my time at Berkeley, I learned that I love to challenge myself. I switched into a more difficult major, did not hesitate to take demanding classes, and did all I could to demand more of myself. I want to continue to find opportunities to challenge myself after I graduate, and I know that working at MyVest will provide that for me.

\noindent Please feel free to ask me any questions - my contact information can be found here and on my resume. Also, I am located just across the Bay, so I am just a stone's throw away. Thank you for your consideration and time.
 
\closing{Sincerely yours,} 
 

 

\end{letter}
 

\end{document}






