% LaTeX resume using res.cls
\documentclass[margin]{res}
\usepackage{multicol}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-20pt}
\usepackage{etoolbox}
\usepackage{ragged2e}
\AtBeginEnvironment{multicols}{\RaggedRight}
\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Patrick N. Yu}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{2515 Benvenue Ave}
 \moveleft.5\hoffset\centerline{Berkeley, CA 94704}
 \moveleft.5\hoffset\centerline{patrick.n.yu@berkeley.edu}
 \moveleft.5\hoffset\centerline{(714) 651-5438}



\begin{resume}

\section{EDUCATION} {\sl Bachelor of Arts,} Applied Mathematics \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                University of California, Berkeley\\
                Expected: May 2015 \\
                Concentration: Computer Science \\
 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} Python, Java, Matlab, 
         Scheme, Latex, R, Ruby, Git\\
                {\sl Operating Systems:} Windows, Mac, Unix
								
\section{MAJOR \\ CLASSES}             
               \begin{multicols}{2}
	       \begin{itemize}\itemsep -2pt
		\item Multivariable Calculus\\
 		\item Linear Algebra 
		\item Differential Equations\\
		\item Discrete Mathematics\\
                \item Real Analysis\\
                \item Abstract Algebra\\
		\item Cryptography\\
		\item Numerical Analysis\\
                \item Complex Analysis\\
                \item Structure of Computer Programs\\
		\item Data Structures\\
                \item Efficient Algorithms\\
		\item Probability and Random Processes\\
                \item Computing with Data\\
		\end{itemize}
	       \end{multicols}
\section{EXPERIENCE} {\sl Social Coordinator, Treasurer, Head Coordinator} \hfill            2013 - 2015\\
                Project S.M.I.L.E.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Board member for Project S.M.I.L.E. and
                                held a variety of positions.
                \item Worked closely with the ASUC, LEAD Center, and Public Service Center, handling a variety of aspects of the club.
                 \end{itemize}
                {\sl Seminar Organizer, Education 97/197} \hfill                       2013 - 2015\\
                University of California, Berkeley
                \begin{itemize} \itemsep -2pt
                \item Organized a seminar which brought in speakers for different topics in education.
                \end{itemize}
		%{\sl Treasurer} \hfill 2011 - 2012 \\
                %Hall Association, Residence Hall Assembly \newline
                %Clark Kerr Campus, Berkeley, CA
                % \begin{itemize}  \itemsep -2pt %reduce space between items
                % \item Used the Residence Hall's Ledger system to record all the money
		%						spent by the Residence Hall Assembly and Hall Association
		%						of Clark Kerr Campus Dormitory which housed over 900 students.
                %\end{itemize}
\section{PROJECTS}Image Recognition
		\begin{itemize} \itemsep -2pt
		\item Designed and implemented machine learning algorithms to identity written numbers in images.
		\end{itemize}
		Spam Filter
		\begin{itemize} \itemsep -2pt
		\item Designed and implemented algorithms to create a spam filter for email data.
		\end{itemize}
		Image compression
		\begin{itemize} \itemsep -2pt
		\item Implemented singular value decomposition processes to create a percentage based image compression program to decrease the storage size for the image.
		\end{itemize}
		Heat Maps
		\begin{itemize} \itemsep -2pt
		\item Executed Crank-Nicolson finite difference method to solve the heat equation and track smells moving across a room.
		\end{itemize}
		PageRank
		\begin{itemize} \itemsep -2pt
		\item Designed ranking system using a version of the PageRank algorithm that ranked actors using IMDb ratings through the Beautiful Soup Python package.
		\end{itemize}
 
%\section{COMMUNITY \\ SERVICE}  Mentor for Project S.M.I.L.E. 
%								\newline Member of Cal Rotoract
%								\newline Finished a Boy Scout Eagle project where I designed, constructed,
%								and installed three benches at my old elementary school.
 

\end{resume}
\end{document}
